Designing Turk Experiments for Visual Statistical Inference

### 2013-07-22 paper_turk.tex
reviewed upto section 3 (web application)

\subsection{Test and Training Lineup} Some lineups should be displayed for the MTurk worker so that they can become familiar with the experimental environment before they participate the actual experiment. It is important to setup this properly. The training lineups should be easy and feedback should be provided right after the response is received. The purpose is to give them an idea how the actual task would look like. The worker may or may not like to try the training lineups.

The another option is to make this training mandatory to participate the experiment. The MTurk worker should have certain proportion of correct responses on these training lineups to allow them to participate. This is often practiced in MTurk task and the workers are very familiar with this approach. In MTurk language it is called the qualification of the worker. Thus to design a MTurk task it is important to fix a standard qualification of the worker.

Other things that needs to be considered include number of training lineups and how the lineups should be shown. Training should not take much longer. Two or three lineups can provide enough training. The training lineups should be easy to evaluate and they should be randomly selected from a very small number of lineups. That may produce repetition which may help the MTurk workers to retest their skills on the lineup they might have a wrong selection before.

@@

\item {\bf IRB approval:} Since this is a human subject experiment proper approval has to be taken from Institutional Review Board or IRB. This approval includes how the task will be performed, how the anonymity of the subjects will be maintained etc. For this we plan to have a consent form which the MTurk workers have to agree before participating the experiment. The consent form is approved by IRB.

@@

\item {\bf Data input:} For lineup experiments input data  mainly refer to the lineups that are going to be presented for evaluations. Lineups may be presented in some sequence or completely at random. We need to decide whether a test lineup will be included or not in the pool of lineups going to be presented. Some other inputs may accompany with each lineup. Those include lineup question, how many lineups to be evaluated by the worker etc. Anything that the worker will see changing with each lineup is considered as data input to the worker. For different experimental needs this input may be different. For example, one may decide to let the worker know if each evaluation made is correct or wrong after the feedback has been submitted. This is an input for the worker.

@@

\item {\bf Payment:} Payment plays an important role on data quality and how fast the data can be collected. It depends on how many lineups are being evaluated by a worker, how much time it may require to finish the task or how hard the task is in general. The MTurk convention is to pay as per an hourly rate of \$6. But some times it may be more or less depending on the task type. For some easy tasks it may take longer time which will reduce the pay rate by hour. Other tasks which are difficult but can be done very fast will have a increase payment rate.

>>>>

\subsection{Test and Training Lineup} It is desirable that some lineups be displayed to the MTurk workers so that they can become familiar with the experimental environment before they participate the actual experiment. It is important to setup this properly. These training lineups should be easy and feedback should be provided right after the response is received. The purpose is to give them an idea how the actual task would look like. The workers may or may not opt for trying the training lineups.

Another option is to make this training mandatory to participate the experiment. The MTurk workers should have certain proportion of correct responses on these training lineups to be allowed to participate. This is often practiced in MTurk task and the workers are very familiar with this approach. In MTurk language it is called the qualification of the worker. Thus to design a MTurk task it is important to fix a standard qualification of the worker.

Other things that need to be considered include number of training lineups and how the lineups should be shown. Training should not take much longer. Two or three lineups can provide enough training. The training lineups can be randomly selected from a very small number of lineups. That may produce repetition which may help the MTurk workers to retest their skills on the lineup they might have a wrong selection before.

@@

\item {\bf IRB approval:} Since this is a human subject experiment proper approval has to be taken from Institutional Review Board or IRB. This approval includes how the task will be performed, how the anonymity of the subjects will be maintained etc. For this we plan to have a consent form which the MTurk workers have to agree before participating the experiment. The consent form needs to be approved by IRB.

@@

\item {\bf Data input:} For lineup experiments input data mainly refer to the information about lineups that are going to be presented for evaluations. Lineups may be presented in some sequence or completely at random. We need to decide whether a test lineup will be included or not in the pool of lineups going to be presented. Some other inputs may accompany with each lineup. Those include lineup question, how many lineups to be evaluated by the worker etc. Anything that the worker will see changing with each lineup is considered as data input to the worker. For different experimental needs this input may be different. For example, one may decide to let the worker know if each evaluation made is correct or wrong after the feedback has been submitted. This is an input for the worker.

@@

\item {\bf Payment:} Payment plays an important role on data quality and how fast the data can be collected. It depends on how many lineups are being evaluated by a worker, how much time it may require to finish the task or how hard the task is in general. The MTurk convention is to pay as per an hourly rate of \$6. But some times it may be more or less depending on the task type. For some easy tasks it may require longer time to evaluate reducing the pay rate by hour. Other tasks which are difficult but can be done very fast will have a increase payment rate.
